Nested sampling with two objective functions

### 2015-10-30 Paper/ms.tex
working on Skilling's argument

The following argument is due to John Skilling. Consider Bayesian model selection
between two models $M_1$ and $M_2$. The Bayes Factor is the ratio of the
two marginal likelihoods:

\begin{eqnarray}
B = \frac{P(D | M_1)}{P(D | M_2)} = \frac{Z_1}{Z_2}
\end{eqnarray}
In large problems, the log of the Bayes Factor is usually more convenient:

\begin{eqnarray}
\ln B = \ln Z_1 - \ln Z_2.
\end{eqnarray}

Naively, we want $\ln B$ to an accuracy of about 0.1, so that we can reliably
quantify the strength of the evidence when the two models are similarly
supported by the data.

Use Skilling's argument about the prior distribution of a log Bayes factor.
Even though the performance of this algorithm won't be great for high $H$, it
will be good enough. I think the probability it won't give enough accuracy will
be ``exponentially small''.

>>>>

The following argument is due to John Skilling. Consider Bayesian model selection
between two models $M_1$ and $M_2$. The Bayes Factor is the ratio of the
two marginal likelihoods:
\begin{eqnarray}
B = \frac{P(D | M_1)}{P(D | M_2)} = \frac{Z_1}{Z_2}
\end{eqnarray}
In large problems, the log of the Bayes Factor is usually more convenient:
\begin{eqnarray}
\ln B = \ln Z_1 - \ln Z_2.
\end{eqnarray}
Naively, we want $\ln B$ to an accuracy of about 0.1, so that we can reliably
quantify the strength of the evidence when the two models are similarly
supported by the data. But is this a realistic situation?
Prior to the data, we don't know the
value of $\ln B$. Rather, $\ln B$ has a prior distribution:
\begin{eqnarray}
P(\ln B \in R) &=& \int P(D)P(\ln B \in R | D) \, dD\\
&=& \int P(D) \mathds{1}\left(\ln B(D) \in R\right) \, dD\\
&=& \int \sum_{i\in\{1,2\}}\left[P(M_i)P(D|M_i)\right] \mathds{1}\left(\ln B(D) \in R\right) \, dD
\end{eqnarray}

%Use Skilling's argument about the prior distribution of a log Bayes factor.
%Even though the performance of this algorithm won't be great for high $H$, it
%will be good enough. I think the probability it won't give enough accuracy will
%be ``exponentially small''.
